---
title: "Practice Survival PYQ"
author: "Ahmad Firdaus Mohamed"
date: "2024-01-22"
output: word_document
---

# Survival Analysis

# Load Library

```{r}
library(survival)
library(gtsummary)
library(survminer)
library(tidyverse)
library(broom)
library(lubridate)
library(haven)
library(dplyr)
library(corrplot)
library(mfp)
```

## Read Data

```{r}
stroke <- read_dta ("stroke_outcome.dta")
```

```{r}
summary(stroke)
```

```{r}
stroke <- stroke %>%
  mutate_if(is.labelled,~as_factor(.))
```

```{r}
summary(stroke)
```

```{r}
stroke <- stroke %>%
  mutate(dur=stroke$doa %--% stroke$dod) %>%
           mutate(dur=as.duration(dur)) %>%
  mutate(dur_days = dur/ddays (1))

```

```{r}
stroke <- stroke %>% 
  mutate(category=cut(stroke$sbp, c (0,140,160,300), label = c('normal', 'hpt1','hpt2')))
  
```

```{r}
KM1 <- survfit(Surv(time = dur_days, event == 'dead')~1, type= "kaplan-meier", data = stroke)
summary(KM1)
```

```{r}
plotKM <- ggsurvplot(KM1, conf.int = TRUE, surv.median.line = "hv", xlab="days") ##surv.median.line = "hv", xlab("Days"), ylab= "survival probability", break.time.by = 20, risk.table =T)
plotKM
```

```{r}
quantile (KM1, probs = c (0.25,0.50, 0.75))
```

```{r}
summary(KM1, times = c(10, 20, 30))
```

```{r}
KMlogrank <- survdiff(Surv(time = dur_days, event == "dead")~sex, data = stroke, rho = 0)
KMlogrank
```

```{r}
KMpeto <- survdiff(Surv(time = dur_days, event == "dead")~sex, data = stroke, rho = 1)
KMpeto
```

p\>0.05, hence there is no difference between survival probability of male and female

Efron Method

```{r}
cox1 <- coxph(Surv(time = dur_days, event == "dead")~sex + sbp + sex:sbp, data = stroke)
cox1
```

Breslow Method

```{r}
cox2 <- coxph(Surv(time = dur_days, event == "dead")~sex + sbp + dm2, data = stroke, method = 'breslow')
cox2
```

```{r}
cox3 <- coxph(Surv(time = dur_days, event == "dead")~sex + sbp + dm2, data = stroke, method = 'breslow')
cox3
```

```{r}
tidy(cox3, conf.int = TRUE)
```

Interaction

```{r}
cox4 <- coxph(Surv(time = dur_days, event == "dead")~sex + sbp + dm2 + sex:dm2, data = stroke, method = 'breslow')
cox4
```

```{r}
anova (cox2, cox4, test = 'Chisq')
```

Checking assumption for CoxPH

Multicollinearity (there is no need check due to only 1 covariate, sbp)

```{r}

```

Proportional hazard

```{r}
cph <- cox.zph(cox2, transform = 'km', global = TRUE) ## can use transform=identity / log/km
cph
plot(cph)
```

All p-value are \> 0.05 and global is \>0.05, hence the proportional hazard is met.

Plots show some violation (appear outside line) but not severe.

Linearity

```{r}
mfp.sbp <- mfp(Surv(time = dur_days, event == 'dead' )~fp (sbp, df=4) + sex + dm2 + dm2, family = cox, data = stroke, verbose = TRUE)
```

```{r}
mfp.sbp$pvalue
```

p-value of p.lin is \>0.05 (0.17), hence linearity is assumed

Residuals

```{r}
score.cox <- resid(cox2, type = "score")
plot(score.cox)
```

```{r}
marti.cox <- resid(cox2, type = "martingale")
plot(marti.cox)
```

```{r}
sch.cox <- resid(cox2, type = "schoenfeld")
plot(sch.cox)
```

```{r}
scaled.cox <- resid(cox2, type = "scaledsch")
plot(scaled.cox)
```

Checking for every covariate (we should do for all covariate, kalau x mention dia akan ambik yang paling atas)

```{r}
marti.sex <- resid(cox2, type = "martingale")
plot(stroke$sex, marti.cox)
```

\
Getting residual using augment

```{r}
augment(cox2, data = stroke)
```

```{r}
new.data <- expand.grid(sbp = c(110, 150, 170), sex= c('male','female'), dm2 = c ('yes','no'))
new.data
```

```{r}
augment(cox2,new_data=new.data)
```

So, to predict using new data

```{r}
summary(cox2)
```

```{r}
tidy(cox2)
```

Equation = 0.1396\*sex + 0.0053\*sbp + 0.9525\*dm

```{r}
(0.1396*0) + (0.0053*108) + (0.9525*0)
```

Log Hazard

```{r}
predict(cox2, newdata = new.data, type = 'lp')
```

Hazard Risk

```{r}
predict(cox2, newdata = new.data, type = 'risk')
```

Create Table

```{r}
Tbl1 <- tbl_regression(cox2, pvalue_fun = ~style_pvalue(.x, digits = 3))
Tbl1
```